\documentclass[../monografia.tex]{subfiles}
\graphicspath{ {images/}{../images/}{../../images/} }

% ---
% RESUMOS
% ---

\begin{document}

    \clearpage

    {\centering   
        \chapter*{Resumo}
    }
     The usage of autonomous devices is growing in number of devices and applications. For having a specific purpose with hardware processing execution, it is classified as an embedded system. In this scope, the realization of all tests to determine the execution, safety and reliability of the system, to guarantee the exact integration between the physical environment  and the implemented software, are of extreme importance. To avoid the dependency to the electronics, the implementation of a simulated system to validate the software is useful and necessary.With the using of QEMU for hardware emulation and Gazebo to simulate the environment, the project looks for a way to develop and have a full first trial test of an embedded system without needing the presence of any electronic component.
    
     \textbf{Palavras-chave}: latex. abntex. editoração de texto.
        
    \clearpage
    
    \begin{minipage}{\textwidth}
        {\centering   
        \chapter*{Abstract}
        }
        \hspace{1cm} The usage of autonomous devices is growing in number of devices and applications. For having a specific purpose with hardware processing execution, it is classified as an embedded system. In this scope, the realization of all tests to determine the execution, safety and reliability of the system, to guarantee the exact integration between the physical environment  and the implemented software, are of extreme importance. To avoid the dependency to the electronics, the implementation of a simulated system to validate the software is useful and necessary.With the using of QEMU for hardware emulation and Gazebo to simulate the environment, the project looks for a way to develop and have a full first trial test of an embedded system without needing the presence of any electronic component.
    
       \vspace{\onelineskip}
     
       \noindent 
       \textbf{Keywords}: latex. abntex. text editoration.
    \end{minipage}
\end{document}